\documentclass{resume} % Use the custom resume.cls style
\usepackage{scrextend}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\addtokomafont{labelinglabel}{\sffamily}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.25\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Gulnara Sungatullina} 
\address{\space+79196827058 \\ sungatullina.gg@phystech.edu \\ t.me/Julnara \\ \textcolor{blue}{\href{https://github.com/sungulnara2000}{github.com/sungulnara2000}}}
\begin{document}
\begin{rSection}{Education}
{\bf Moscow Institute of Physics and Technology, Russia} \hfill {\em Sep 2018 - July 2022} 
\\ Bachelor in Applied Mathematics and Computer Science
\\ Department of Innovation and High Technology
\\ GPA: 4.6/5
\\ {\bf Relevant courses}: Algorithms \& Data Structures, C++, Computer Architecture \& Operating Systems, Databases, Discrete Analysis, Algebra, Calculus, Probability, Differential Equations, Programming Technology.
\\{\bf Extra}: Deep Learning School (ML basics, pytorch, optimizations, CV)
\end{rSection}

\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{9ex}} l }
Languages \ & proficient in C++(Boost, STL), confident in Python(pytorch, sklearn), C, C\#,
\\ &  SQL, familiar with Bash, ARM/x86 Assembly \\
Technologies \ & experienced with Git, Linux, PostgreSQL, Jupyter, Colab, Docker
\\ & familiar with Amazon Web Services, Travis CI \\
\end{tabular}
\end{rSection}

\begin{rSection}{Projects}
\begin{multicols}{2}
{\bf HR database} (SQL) 
\vspace{-2mm}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Designed a normalized database and filled it in.
    \item Created views, triggers, and procedures in order to simplify the work of labor officers.
\end{itemize}

{\bf Telegram Compiler bot} (Python)
\renewcommand\labelitemi{\tiny$\bullet$}
\vspace{-2mm}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Developed a telegram bot, which helps to compile and receive program output via messenger.
    \item Used REST API of an online compiler site  for proper functioning.
    \item Set up AWS Virtual Machine for maintaining constant work.
\end{itemize}

{\bf \textcolor{blue}{\href{https://github.com/sungulnara2000/Journey-To-Springfiled/blob/master/Journey_to_Springfield.ipynb}{Journey to Springfield}}} (Python/pyTorch)
\renewcommand\labelitemi{\tiny$\bullet$}
\vspace{-2mm}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item convolutional classifier to distinguish all Springfield residents from the picture
    \item 0.96 score on Kaggle(top 72\%)
\end{itemize}


{\bf \textcolor{blue}{\href{https://github.com/sungulnara2000/TravellingSalesmanProblem/tree/master/salesman_travis}{Travelling Salesman Problem}}} (C++)
\vspace{-2mm}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Implemented 3/2-approximate algorithm for metric Travelling Salesman Problem.
    % \item Tested on normally distributed points.
\end{itemize}

{\bf \textcolor{blue}{\href{https://github.com/sungulnara2000/RPG}{RPG game}}} (C\#/Visual Studio)
\vspace{-2mm}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Designed and created an RPG game with simple graphical interface.
    % \item The selected character is controlled using the keyboard arrows.
    \item Used design patterns to improve project structure.
\end{itemize}



\end{multicols}
\end{rSection}


\begin{rSection}{Achievements}
\begin{rSubsection}{National Technological Initiative Olympiad $|$ Unmanned aircraft systems}{\em March 2018}{first in the team competition, individual prize-winner}{Moscow, Russia}
\renewcommand\labelitemi{\tiny$\bullet$}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Simulated and programmed(C++) a mathematical model of airplane flight.
    \item Launched an airplane model and reached 5\% deviation from the perfect flight path.
    \item Beat 9 other teams by a landslide.
\end{itemize}
\end{rSubsection}


{\bf Olympiad of MIPT $|$ Mathematics} - {\em first degree diploma} \hfill{\em Feb 2018}

\end{rSection}

\begin{rSection}{Personal}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Spoken languages \ & English - B2, Russian - native, Tatar - native 
% \\Hobbies \ & singing, cooking, work-out, 
\end{tabular}
\end{rSection}

\begin{rSection}{Activities}
\renewcommand\labelitemi{\tiny$\bullet$}
\begin{itemize}[noitemsep, parsep=0pt, leftmargin=*]
    \item Organized MIPT Olympiad for more than 100 schoolchildren.
    \item {\bf Hach\&Change hackathon}: solved the problem of placing self-pickup points using Voronoi diagram and ML algorithms.
\end{itemize}
\end{rSection}

\end{document}